---
title: "Data science end-to-end Walkthrough"
subtitle: "In-database analytics with and R and SQL server"
venue: "ITViate data science courses"
type: "invited"
recording: "none"
output:
  ioslides_presentation:
    transition: default
    widescreen: true
    standalone: false
css: styles.css
date: "Slides -- <http://bit.ly/2q9NPSU>  <br /> <br />"
author: "Hicham Zmarrou"
---


```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  fig.width = 10,
  fig.height = 4,
  comment = "#>",
  collapse = TRUE,
  warning = FALSE
)
```

        
## Aims of this lesson 

+ Give you a general introduction to neural networks, How they works and how to implement them in  `R`. 



## What are Neural networks

https://www.youtube.com/watch?v=bxe2T-V8XRs

https://www.youtube.com/watch?v=UJwK6jAStmg

https://www.youtube.com/watch?v=5u0jaA3qAGk&t=45s

https://www.youtube.com/watch?v=GlcnxUlrtek

https://www.youtube.com/watch?v=pHMzNW8Agq4

https://www.youtube.com/watch?v=9KM9Td6RVgQ

https://www.youtube.com/watch?v=S4ZUwgesjS8



## Neural network from scratch

```{r, echo=FALSE}
library(ggplot2)
moons <- read.csv("./data/moonsXY.csv")
#moons[,1] <- NULL 
sp<-ggplot(moons, aes(x=xcoord, y=ycoord, color=as.factor(label))) + geom_point()
sp
```

+ The dataset we generated has two classes, plotted as red and blue points. 

+ You can think of the blue dots as male patients and the red dots as female patients, with the x- and y- axis being medical measurements.

